Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-11-07 draft.tex
revise def of SQ eqm, minor grammatical revisions

Our concept of equilibrium will be stationary Markov equilibrium as defined in Mailath and Samuelson (2006). That is, a strategy profile is a stationary Markov equilibrium if it is a stationary Markov strategy profile and a subgame-perfect equilibrium. In turn, a strategy profile is defined to be a stationary Markov strategy if any two ex post histories terminating in the same state play identically from the termination point forward. That is, stationary Markov strategies ignore all details of the history aside from the current state.

@@

In equilibrium, the outside actors' investments are paired: the patron investments in the secessionists' status quo payoffs deter player $c$'s investments in the secessionists' payoffs from ceding. Likewise, investments by player $c$ in the government's status quo payoffs deter the patron from investing in the government's payoffs from ceding. Investments by player $c$ in the secessionists' status quo payoffs deter the patron from investing in the secessionists' payoffs from winning the conflict via fighting. In each case, the investments are sufficient to make the largest continuation payoffs in the game between the secessionists and the government those from playing status quo.

\begin{definition}
The Status Quo Equilibrium is a stationary Markov equilibrium in which the outcome is perpetual unrecognized statehood. The strategy profiles are the following, organized according to the patron's investments in each state variable. In period $t$:

@@

If $R_{pt} > \frac{1}{p_{1s}}\left[\frac{\nu p_{1s} - \beta (1-p_{1s})}{1 -\de} - \mu + Q_{s,t-1} - \left(-\zeta_{s}(1-\de) + W_{s,t-1}p_{1s} + L_{s,t-1}(1-p_{1s})\right)\right] $ to augment $w_{s,t}$, player $c$ will choose $R_{ct}=0$. Fight becomes the unique best response for the secessionists.
\end{enumerate}
The government and secessionists play their best responses in the stage game given the continuation values induced by the investments of the outside actors. Unless otherwise noted above, playing Status Quo is the best response for both inside actors.
\end{definition}

>>>>

Our concept of equilibrium will be stationary Markov equilibrium as defined in Mailath and Samuelson (2006). That is, a strategy profile is a stationary Markov equilibrium if it is a stationary Markov strategy profile and a subgame-perfect equilibrium. In turn, a strategy profile is defined to be a stationary Markov strategy if any two ex post histories terminating in the same state play identically from the termination point forward. In other words, stationary Markov strategies ignore all details of the history aside from the current state.

@@

In equilibrium, the outside actors' investments are paired: the patron's investments in the secessionists' status quo payoffs deter player $c$'s investments in the secessionists' payoffs from ceding. Likewise, investments by player $c$ in the government's status quo payoffs deter the patron from investing in the government's payoffs from ceding. Investments by player $c$ in the secessionists' status quo payoffs deter the patron from investing in the secessionists' payoffs from winning the conflict via fighting. In each case, the investments are sufficient to make the largest continuation payoffs in the game between the secessionists and the government those from playing status quo.

\begin{definition}
A Status Quo Equilibrium is a stationary Markov equilibrium in which the outcome is perpetual unrecognized statehood.

The strategies for the government and secessionists in this equilibrium are to play their best responses in the stage game given the continuation values induced by the investments of the outside actors. Unless otherwise noted below, playing Status Quo is the best response for both inside actors. The strategies for the insides actors are the the following, organized according to the patron's investments in each state variable. In period $t$:

@@

If $R_{pt} > \frac{1}{p_{1s}}\left[\frac{\nu p_{1s} - \beta (1-p_{1s})}{1 -\de} - \mu + Q_{s,t-1} - \left(-\zeta_{s}(1-\de) + W_{s,t-1}p_{1s} + L_{s,t-1}(1-p_{1s})\right)\right] $ to augment $w_{s,t}$, player $c$ will choose $R_{ct}=0$. Fight becomes the unique best response for the secessionists.
\end{enumerate}
\end{definition}
